Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Completes first pass of SoA. Still one to go

% This reference is not terribly relevant
PCG methods are also used in different contexts: Y. Jiang et al. \cite{Jiang2017}
proposed the use of predefined letter patterns and combined them to create a
small pool of words and letters used to create levels with text on them.
Users would play the game, and after that,   asked them if they liked the
layout of the Levels.
% ----------------------------------------
    \section{Proposed Method}
    \label{prop_method}

>>>>

The objective of generating levels need not be pure gameplay or enjoyment. Angry Birds have been also used for trying to promote mental well-being, the point of it being that the game can be used as a vehicle for art therapy \cite{fang2019angrybirdslike}. Instead of using a search-based approach, levels are generated from sketches drawn by the patient using a method called Real Pixel Image Level Generator; the main objective is to get the players to smile. This interesting approach of using some external input to generate levels could be adapted or integrated easily into search-based approaches; at the same time, it is a way of exploring how to elicit different response from game players.

% This reference is not terribly relevant
PCG methods are also used in different contexts: Y. Jiang et al. \cite{Jiang2017}
proposed the use of predefined letter patterns and combined them to create a
small pool of words and letters used to create levels with text on them.
Users would play the game, and after that,   asked them if they liked the
layout of the Levels. This interactive approach could, in principle, be also apprached in the generation of Angry Birds levels.

In our case, interaction is not required or used; our main intention is to generate interesting and aesthetically pleasing levels. The methodology to achieve this is explained below.

% ----------------------------------------
    \section{Proposed Method}
    \label{prop_method}
